---
output: github_document
---
  
<!-- README.md is generated from README.Rmd. Please edit that file -->
  
```{r,echo=FALSE}
knitr::opts_chunk$set(collapse=TRUE,comment='#>',fig.path='README-')
```

[![Travis-CI Build Status](https://travis-ci.org/sw1/theseus.svg?branch=master)](https://travis-ci.org/sw1/theseus)
[![codecov](https://codecov.io/gh/sw1/theseus/branch/master/graph/badge.svg?token=pmjXMfuHrw)](https://codecov.io/gh/sw1/theseus)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/theseus)](https://cran.r-project.org/package=theseus)


## Overview
<!-- same text as "description" in DESCRIPTION, just as a (temporary) placeholder. once it's up and running we can flesh some of this out. -->
theseus provides functions to assist in the analysis, visualization, and interpretation of community composition data, especially those originating from amplicon sequencing.  

## Relevant Software and Literature    
* Price, Woloszynek, Rosen, and Sales (2018) [theseus - An R package for the analysis and visualization of microbial community data](https://www.biorxiv.org/content/early/2018/04/05/295675)    
* Callahan, Sankaran, Fukuyama, McMurdie, and Holmes (2017) [Bioconductor Workflow for Microbiome Data Analysis: from raw reads to community analyses](http://dx.doi.org/10.12688/f1000research.8986.2)     
*  McMurdie and Holmes (2013) [phyloseq: An R package for reproducible interactive analysis and graphics of microbiome census data](http://dx.plos.org/10.1371/journal.pone.0061217)    
* Oksanen,Blanchet, Friendly, Kindt, Legendre, McGlinn, Minchin, O'Hara, Simpson, Solymos, Stevens, Szoecs, and Wagner (2017) [vegan: Community Ecology Package](https://CRAN.R-project.org/package=vegan)  


## Installation

```{r,eval=FALSE}
# To install the release version of theseus:
install.packages('theseus')

# To install the developmental version via Github:
# install.packages('devtools')
devtools::install_github('EESI/theseus',build_vignettes=TRUE)
```

## Development

For future feature requests or suggestions, request an issue:
  
  https://github.com/EESI/theseus/issues